\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-17 ms/adult.tex
Fix multiply-defined fig labels
Add barplot for tendency to consume porn
Add barplot for tendency to consume porn, split by party.

\begin{figure}[ht]
\centering
\caption{Quantile Estimates--Hours Spent on Adult Sites by Party}
\includegraphics[width=.6\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
}
\label{fig:quantile_regression_duration}
\end{figure}

\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party}
	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

These minor differences (or lack of differences) could be because of the demographic differences we see across the party. Next, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much. Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find.

@@

@@

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_duration_nonzeroes}
\end{figure}

@@

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_duration_nonzeroes_covariates}
\end{figure}
\FloatBarrier
%===============================================================================
% Analogous results for visits to adult sites
%===============================================================================
\section{Analysis of Visits}

>>>>

%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[ht]
\centering
\caption{Quantile Estimates--Hours Spent on Adult Sites by Party}
\includegraphics[width=.6\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
}
\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party}
	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

These minor differences (or lack of differences) could be because of the demographic differences we see across the party. This lack of difference also partly stems from a lack of difference in the tendency to consume pornography (see \cref{fig:consume_porn_yes_no}). Next, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much. Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find.

@@

%===============================================================================
\begin{figure}
	\centering
	\caption{Porn Consumption by Party}
	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows proportion of panelists in the sample who ever consumed pornography in the sample period by party.
		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:consume_porn_yes_no}
\end{figure}

@@

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_duration_nonzeroes_covariates}
\end{figure}

@@

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_duration_nonzeroes_covariates}
\end{figure}
\FloatBarrier
%===============================================================================
% Analogous results for visits to adult sites
%===============================================================================
\section{Analysis of Visits}
